### 2020-08-07 spinors.tex
change the font and style

\subsection{Convention \TODO{WIP!}}
First we prepare a vector $x^\mu$ and a symmetric matrix $\eta^{\mu\nu}$, which we call ``contravariant vector'' $x^\mu$ and the metric $\eta^{\mu\nu}$.
Then we perform a Lorentz transformation on $x^\mu$ to obtain $(x')^\mu$, with which we can define a matrix $\Lambda(\vc va,\vc \theta)^{\mu}_{\nu}$ through 
$\Lambda{}^\mu{}_\nu x^{\nu}=(x')^{\mu}$.

>>>>

\subsection[Convention]{Convention \TODO{WIP!}}
First we prepare a vector $x^\mu$ and a symmetric matrix $\eta^{\mu\nu}$, which we call ``contravariant vector'' $x^\mu$ and the metric $\eta^{\mu\nu}$.
Then we perform a Lorentz transformation on $x^\mu$ to obtain $(x')^\mu$, with which we can define a matrix $\Lambda(\vc va,\vc \theta)^{\mu}_{\nu}$ through 
$\Lambda{}^\mu{}_\nu x^{\nu}=(x')^{\mu}$.
